% Autogenerated translation of index.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
title: EMPLOYMENT EXPERIENCE

\section*{date: 2019-03-24 02:56:33}

I have worked in 2 companies in field of smart grid and Internet. In the future, I wish to work in internet companies as data analyst and consultant.

\chapter*{\texttt{$<$font color=\#EC552D$>$} Mobike \texttt{$<$/font$>$}}

\emph{Intern of department of Data Analysis \& Business Intelligence, Beijing, China}
\emph{From June 2018 to Sep. 2018}

\href{https://mobike.com/global/}{Mobike} is an internet technology company offers bike sharing service to fulfil urban short trips. As an intern in Department of Data Analysis, I:
* Operate, test, design internal data system (Product Manager).
* Operate and Design internal data producing environment for BI (Product Manager).
* Design Wechat Mini Program to display operation index \& data.
* Design Data Platform APP.
* Offer solution to data-related requirements as a Data Analyst.

\chapter*{\texttt{$<$font color=\#1D5396$>$} NARI \texttt{$<$/font$>$}}

\emph{Intern of Department of System Integration, Nanjing, China}
\emph{From July 2017 to Aug. 2017}

\href{http://www.narigroup.com/}{NARI} is a technology company offers intelligent industrial equipments ranging from power electronics to water conservancy and rail transit. As an intern, I:
* Operate, assemble Linux Server.
* Assemble smart grid operation sofware system.

\end{document}
